### 2022-06-22 proposal-documents/white-paper/white-paper-phd-proposal.tex

%%%%% references
%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
%%%%%

%%%%% tables and figures
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage{tablefootnote}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{tabto} %general tabbed spacing

\usepackage[singlelinecheck=false,labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format

\usepackage{wrapfig} %wraps figures around text
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}
%%%%%

\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
\usepackage[inline]{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{lscape}
\usepackage{array}
\usepackage{chngcntr}
\usepackage[hidelinks]{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
\usepackage[toc,page]{appendix}
\usepackage[figure,table]{totalcount}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

\usepackage[firstpage]{draftwatermark}
%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
%\SetWatermarkScale{0.35}

\usepackage{wrapfig}
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}

@@

\makeatletter
\renewcommand\section{%
    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
    {\Large \normalfont \bfseries}}%

\makeatletter
\renewcommand\paragraph{%
    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
    {\normalfont \normalsize \bfseries}}%

\makeatletter
\renewcommand\subparagraph{%
    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
    {\normalfont \normalsize \itshape }}%

\makeatletter
\renewcommand\subsection{%
    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
    { \large \normalfont \bfseries}}%

\setlength{\bibsep}{0pt} %sets space between references
\renewcommand{\bibsection}{} %suppresses large 'references' heading
\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize Title Keyword}
\chead{\scriptsize \textit{Name - PhD White Paper Project Proposal}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

@@

\begin{center}\subsection*{Abstract}\end{center}

\paragraph*{Summary of the Proposed Project.}

\paragraph*{Motivation.}

\paragraph*{Overall Objective.}

\paragraph*{Importance and Relevance to Objectives.} 
\subparagraph*{Background.}

\subparagraph*{Relevant literature.}

%for a 3 page preproposal, limit above subject matter to the first page

\paragraph*{Logical Path, Work Scope, Description of Tasks.}

\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Title.}
    \item\textit{Title.}
    \item\textit{Title.}
\end{enumerate}

\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Title.}
    \item\textit{Title.}
    \item\textit{Title.}
\end{enumerate}

\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Crosscutting issues.}
\end{enumerate}

\paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
The following outcomes are anticipated - 
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
    \item Identify lessons learned and engage in future pathways and partnerships.
\end{enumerate}

@@

%remove page break if there are page limits
%\vspace{0.5\baselineskip}

\paragraph*{References}
\bibliographystyle{nsf}
\setlength{\bibhang}{0pt}
\bibliography{references}

>>>>

%%%%% references
%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
%\setlength{\bibsep}{7pt} %sets space between references
\renewcommand{\bibsection}{} %suppresses large 'references' heading
%\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
%%%%%

%%%%% tables and figures
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage{tablefootnote}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{tabto} %general tabbed spacing
\usepackage{pdfpages}

\usepackage{wrapfig} %wraps figures around text
\setlength{\intextsep}{0.05mm}
\setlength{\columnsep}{0.05mm}

\usepackage[singlelinecheck=false,labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format

%\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=1pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
%\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Tab.}} %sets space above caption, 'figure' format
%%%%%

\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
\usepackage[inline]{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{lscape}
\usepackage{array}
\usepackage{chngcntr}
\usepackage[hidelinks]{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
\usepackage{marginnote}
\usepackage{gensymb}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
\usepackage[toc,title]{appendix}
\usepackage[figure,table]{totalcount}

\usepackage[capitalise]{cleveref}

%%%%% watermark
%\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
%\SetWatermarkScale{0.25}
%%%%%

@@

%\makeatletter
%\renewcommand\section{%
%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
%    {\large \normalfont \bfseries}}%

%\makeatletter
%\renewcommand\paragraph{%
%    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
%    {\normalfont \normalsize \bfseries}}%

%\makeatletter
%\renewcommand\subparagraph{%
%    \@startsection{subparagraph}{5}{\z@ }{0.40\baselineskip}{-1em}
%    {\normalfont \normalsize \itshape }}%

%\makeatletter
%\renewcommand\subsection{%
%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
%    {\large \normalfont \bfseries}}%

%%%%% header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize Title Keyword}
\chead{\scriptsize \textit{Name - PhD White Paper Project Proposal}}
\rhead{\scriptsize \today}
\rfoot{\thepage}
%%%%%

@@

\section*{Summary of the Proposed Project}

\section*{Motivation}
\subsection*{Context}

\section*{Overall Objective}

\section*{Importance and Relevance to Objectives} 
\subsection*{Background}

\subsection*{Relevant literature}

\section*{Research Workscopes \& Tasks}
\subsection*{Research activities}

\subsection*{Workscope 1 - Title}
\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{First task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
    \item\textit{Second task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
\end{enumerate}

\vspace{0.05in}

\noindent\textit{Through this Workscope, we will \ldots.}

\subsection*{Workscope 2 - Title}
\begin{enumerate}[resume,topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Next task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
    \item\textit{Next task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
\end{enumerate}

\vspace{0.05in}

\noindent\textit{Through this Workscope, we will identify plant systems vulnerable to cyberattacks applying a risk-informed approach and operate the reactor to collect relevant plant data.}

\section*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
The following outcomes are anticipated - 
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
    \item
    \item
    \item
    \item Identify lessons learned and engage in future pathways and partnerships.
\end{enumerate}

@@

\part*{References}
\bibliographystyle{nsf}
\setlength{\bibhang}{0pt}
\bibliography{references}

%\newpage

%\begin{appendices}

%    \renewcommand{\thesection}{\Roman{section}}
%    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]

%\section{Title}\label{app-}

%\end{appendices}
